\documentclass{article}
\usepackage[left=35mm,margin=20mm]{geometry}
\usepackage{ifthen,empheq}
\date{\today}
\usepackage{fancyhdr}
\usepackage[]{dot2texi}
\setlength{\headheight}{15pt}

\lhead{Assignment 1}
\chead{Dilawar Singh}
\rhead{\today}

\lfoot{}\cfoot{\thepage}\rfoot{}
\pagestyle{fancy}

\ifx\pdfoutput\undefined                         %LaTeX
  \RequirePackage[ps2pdf,bookmarks=true]{hyperref}
  \hypersetup{ %
    pdfauthor   = {\@author},
    pdftitle    = {\@title},
    pdfcreator  = {LaTeX with hyperref package},
    pdfproducer = {dvips + ps2pdf}
  }
\else                                            %PDFLaTeX
  \RequirePackage[pdftex,bookmarks=true]{hyperref}
  \hypersetup{ %
    pdfauthor   = {\@author},
    pdftitle    = {\@title},
    pdfcreator  = {LaTeX with hyperref package},
    pdfproducer = {dvips + ps2pdf}
  }
\pdfadjustspacing=1
\fi

% Set up counters for problems and subsections

\newcounter{ProblemNum}
\newcounter{SubProblemNum}[ProblemNum]

\renewcommand{\theProblemNum}{\arabic{ProblemNum}}
\renewcommand{\theSubProblemNum}{\alph{SubProblemNum}}

\newcommand*{\anyproblem}[1]{\newpage\subsection*{#1}}
\newcommand*{\problem}[1]{\stepcounter{ProblemNum} %
   \anyproblem{Problem \theProblemNum. \; #1}}
\newcommand*{\soln}[1]{\subsubsection*{#1}}
\newcommand*{\solution}{\soln{Solution}}
\renewcommand*{\part}{\stepcounter{SubProblemNum} %
  \soln{Part (\theSubProblemNum)}}

\renewcommand{\theenumi}{(\alph{enumi})}
\renewcommand{\labelenumi}{\theenumi}
\renewcommand{\theenumii}{\roman{enumii}}
\begin{document}

\problem{Decoding}

Consider the following set of codewords:

(A,B,C,D,E,F,G,H) = (01, 11, 001, 0000, 0001, 1001, 1010, 1011).

\begin{enumerate}
    \item Is this an instantaneous (prefix) code?
    \item Verify that it satisfies the Kraft inequality.
    \item Construct a string which has no meaning under this system Transmitting
        information across a channel.
\end{enumerate}

\problem{}
Consider the discrete memoryless channel Y = X + Z (mod 11), where Z
is uniformly distributed on the alphabet {1, 2, 3}.

\begin{verbatim}
    1       2       3 
    1/3     1/3     1/3
\end{verbatim}

and $X \in \{0, 1, \ldots 10\}$ . Assume that Z is independent of X.

a. Find the capacity.
b. What is the maximizing p∗(x)?

\problem{}

The Z channel has binary input and output alphabets and transition
probabilities $p(y|x)$ given by the following matrix: Q =

        1   0
        1/2 1/2

$x, 𝑦 \in \{0, 1\}$.

[Why is it called the Z-channel?]
Find the capacity of the Z channel and the maximizing input probability distribution.

\problem{}

[Optional] For the Z channel of the previous problem, assume that we choose a
($2^{nR}$) code at random, where each codeword is a sequence of fair coin
tosses. This will not achieve capacity. Find the maximum rate R such that the
probability of error $P_e^n$ , averaged over randomly generated codes, tends to
zero as the block length n tends to infinity.

\end{document}
