\RequirePackage{luatex85,shellesc}
\documentclass[twocolumn, answers]{exam}
\usepackage[margin=15mm]{geometry}
\usepackage{listings}
\usepackage{pgfplots}
\usepgfplotslibrary{ternary}
\usepackage{concrete}
\usepackage{libertine}
\usepackage{hyperref}
\usepackage{luacode}
\usepackage{fontspec}
\setmonofont{inconsolata}
\lstset{basicstyle=\ttfamily}

\title{Homework 3}
\author{Dilawar Singh}
\date{\today}

% Set up counters for problems and subsections
\begin{document}
\maketitle

\begin{questions}

\question

\textbf{Entropy Rate of Markov Process}

The Morse code uses dots, dashes, and two types of spaces: letter and word
spaces. Spaces only occur as delimiters; that is, no space can follow another
space. What is the entropy rate achievable under these constraints?  Hint: take
a look at Shannon’s 1948 paper for a start, and Example 5.1.3 of C\&T, but use
different notation. Write it out as a Markov process whose states are [.], [-],
[L- space], [W-space]. Assume that all allowed outputs from any state are
equally likely.

\begin{solution}
    
\end{solution}



\question 

\textbf{Large Deviation Theory} We roll a fair six-sided die $n$ times, where
$n$ is large. What is the probability that the number of 2s is at least double 
the number of 1s in the resulting string? Of strings which satisfy this condition, 
what proportion of values will be 1s?

We can split this calculation into the following parts:

\begin{parts}
    
    \part What is the constraint equation for the set $E$ of types (or empirical distributions)
    $P_{x^n}$ which satisfy the required condition?

    \part Let $Q$ be the uniform distribution. Show that the member $P^*$ of $E$
    which minimizes the relative entropy $D(P^*||Q)$ is the maximum entropy
    distribution subject to the constraints from (a).

    \part Find the distribution $P^*$. E.g. let the proportion of 1s be an
    unknown $x$. Use some intuition to set the rest of the distribution. 
    Then use calculus to minimize. You can find the answer analytically.

    \part What is the probability that the outcome of $n$ die rolls belongs to
    $P^*$ (and therefore, to $E$ to first order in the exponent)?

    \part (Optional) Verify your answer for n = 250 by Monte Carlo simulation.

\end{parts}

\end{questions}

\end{document}
